---
title: "CodingChallenge4"
author: "Katie Clouse"
date: "2025-02-27"
output: 
  pdf_document:
  md_document:
    variant: gfm
  html_document:
  toc: true 
  toc_float: true  
---

## Manuscript Link 
[Link to manuscript](https://doi.org/10.1094/PDIS-06-21-1253-RE)

## Question 1

A YAML header is the top 6 lines of the document that explains the logistic information of the document. Literate
programming deals with combining codes and descriptive language in the document so you can have a more inclusive type of document. By having literate programming in R, you can include way more information than just R. 

## Question 2 (reading in mycotoxin data)
```{r}
mico.data <- read.csv("C:/Users/katie/Downloads/MycotoxinData.csv", na.strings = "na")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

## Loading in the packages
```{r}
options(repos = c(CRAN = "https://cloud.r-project.org"))
install.packages("ggpubr")
library(knitr)
library(ggplot2)
library(rmarkdown)
library(ggplot2)
library(tidyverse)
library(ggrepel)
install.packages("ggarrange")
library(ggpubr)

```

## Coding from Coding Challenge 3
```{r}
mico.ques1 <- ggplot(mico.data, aes(x = Treatment, y = DON, color = Cultivar)) + #this defines the aesthetics and allows me to color by cultivar 
  geom_boxplot(position = position_dodge()) + # this provides boxplots that do not overlap 
  geom_point(position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.6)) + #this allows data points that do no overlap 
  ylab("DON(ppm)")+ #this labels the y axis
  xlab("") + #this labels teh x axis
  scale_color_manual(values = cbbPalette, name = "", labels = c("Wheaton", "Ambassador")) + # this gives me colors from the colorblind palette 
  theme_classic() + #this is a classic theme for the plot 
  theme(strip.background = element_blank(), legend.position = "right") + #this puts the legend to the right hand side
  facet_wrap(~Cultivar) #this create separate panels for the cultivar
print(mico.ques1)
```

```{r}
#### Question 2 answers ####

mico.data$Treatment <- factor(mico.data$Treatment, levels = c("NTC", "Fg", "Fg + 37", "Fg + 40", "Fg + 70")) #this rearranges the y labels

mico.ques2 <- ggplot(mico.data, aes(x = Treatment, y = DON, color = Cultivar)) +
  geom_boxplot(position = position_dodge(.6)) + #this adjusts the position of the horizontal bars 
  geom_point(position = position_jitterdodge(.6)) + #this allows the data points to be not overlapping 
  ylab("DON(ppm)")+
  xlab("") +
  scale_color_manual(values = cbbPalette, name = "", labels = c("Wheaton", "Ambassador")) +
  theme_classic() +
  theme(strip.background = element_blank(), legend.position = "right") +
  facet_wrap(~Cultivar)
print(mico.ques2)
```

```{r}
#### Question 3 answers ####

mico.ques3 <- ggplot(mico.data, aes(x = MassperSeed_mg, y = X15ADON, color = Cultivar)) + #this is when you put massperseed_mg on the x axis and X15ADOn is on the y axis 
  geom_boxplot(position = position_dodge(.85)) +
  geom_point(position = position_jitterdodge(.05)) +
  ylab("X15ADON")+
  xlab("Seed Mass (mg)") +
  scale_color_manual(values = cbbPalette, name = "", labels = c("Wheaton", "Ambassador")) +
  theme_classic() +
  theme(strip.background = element_blank(), legend.position = "right") +
  facet_wrap(~Cultivar)
print(mico.ques3)
```


```{r}
#### Question 4 answers ####

figure1 <- ggarrange(mico.ques1, 
                     mico.ques2, 
                     mico.ques3, 
                     labels = "auto", #this labels the plots as A, B, C
                     nrow = 3, 
                     ncol =  1, 
                     common.legend = T) #this allows you to put several plots stacked on top of one another in one column 
print(figure1)

# the common.legend function allows you to utilize only one legend for different plots 
```

```{r}
#### Question 5 answers ####

mico.ques.ttest1 <- mico.ques1 + 
  geom_pwc(aes(group = Treatment, method = "t_test", label = "p.adj.format")) #the geom_pwc is a pairwise comparison test that allows you to compare all treatments against each other 
print(mico.ques.ttest1)

mico.ques.ttest2 <- mico.ques2 +
  geom_pwc(aes(group = Treatment, method = "t_test", label = "p.adj.format"))
print(mico.ques.ttest2)


mico.ques.ttest3 <- mico.ques3 +
  geom_pwc(aes(group = MassperSeed_mg, method = "t_test", label = "p.adj.format"))
print(mico.ques.ttest3)


figure2 <- ggarrange(mico.ques.ttest1, 
                     mico.ques.ttest2, 
                     mico.ques.ttest3,
                     labels = "auto", 
                     nrow = 3, 
                     ncol = 1, 
                     common.legend = T) 
print(figure2)
```

























